Modelling the Co-evolution of Trade and Culture in Past Societies

### 2015-07-01 article.tex
.

\paragraph{Production}
\todo{what is some, what is n}
Each agent produces one good. The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$. At each time step each agent produces $n$ units of its production good, which ensure that he could theoretically trade its production good with every other goods. When an agent consumes its own production good he will automatically reproduce some, so that the consumption does not impact its inventory.

@@

\paragraph{Innovation} In a trading environment it seems unlikely that a price will change radically to a very different value. Therefore, a new and more realistic mechanism is proposed. The innovation process, coined ``self referenced'', is still triggered with probability $\mu$ 
but modifies the previous price by adding or subtracting a small amount taken randomly from a uniform  distribution between $0 .. \beta$.

>>>>

\paragraph{Production}
\todo{what is some, what is n}
Each agent produces one good. The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$. At each time step each agent produces $n$ units of its production good, which ensure that it own theoretically enough of it to trade it with every other goods. Moreover, when an agent consumes its own production good, it doesn't not impact its inventory, meaning that he can produced for free the quantity he consume for itself.

@@

\paragraph{Innovation}

In a trading environment it seems unlikely that a price will change radically to a very different value. Therefore, a new and more realistic mechanism is proposed. The innovation process, coined ``self referenced'', is still triggered with probability $\mu$ 
but modifies the previous price by adding or subtracting a small amount taken randomly from a uniform  distribution between $0 .. \beta$.
